Supplementary Material for `The response of trophic interaction networks to multiple stressors in a marine latitudinal gradient of the Southern Hemisphere'

### 2023-11-27 manuscript.tex
changes SI

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[vmargin=1in,hmargin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{pdflscape,booktabs}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage[running]{lineno}
\linenumbers
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\section{The response of trophic interaction networks to multiple
stressors in a marine latitudinal gradient of the Southern
Hemisphere}\label{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}

@@

\subsection{Abstract}\label{abstract}

@@

\subsection{1. Introduction}\label{introduction}

@@

\subsection{2. The structure of marine food webs in the Southwest
Atlantic - Antarctic
region}\label{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}

@@

\subsection{3. Environmental and anthropogenic stressors in the
Southwest Atlantic - Antarctic
region}\label{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}

@@

\subsubsection{3.1 San Jorge Gulf}\label{san-jorge-gulf}

@@

\subsubsection{3.2 Beagle Channel}\label{beagle-channel}

@@

\subsubsection{3.3 Burdwood Bank}\label{burdwood-bank}

@@

\subsubsection{3.4 Scotia Sea}\label{scotia-sea}

@@

\subsubsection{3.5 Potter Cove
(Antarctica)}\label{potter-cove-antarctica}

@@

\subsubsection{3.6 Weddell Sea
(Antarctica)}\label{weddell-sea-antarctica}

@@

\subsection{4. From species' stressors to food web
effects}\label{from-species-stressors-to-food-web-effects}

@@

\subsubsection{4.1 Main stressors effects on food webs in a southwest
Atlantic - Antarctic
gradient}\label{main-stressors-effects-on-food-webs-in-a-southwest-atlantic---antarctic-gradient}

@@

\subsection{5. Gaps and future
perspectives}\label{gaps-and-future-perspectives}

@@

\subsection{Conclusions}\label{conclusions}

@@

\subsection{Acknowledgements}\label{acknowledgements}

@@

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Acha2004}
Acha, E. M., Mianzan, H. W., Guerrero, R. A., Favero, M., \& Bava, J.
(2004). Marine fronts at the continental shelves of austral {South
America}: {Physical} and ecological processes. \emph{Journal of Marine
Systems}, \emph{44}(1), 83--105.
doi:\href{https://doi.org/10.1016/j.jmarsys.2003.09.005}{10.1016/j.jmarsys.2003.09.005}

\bibitem[\citeproctext]{ref-APN2022}
Administración de Parques Nacionales. (2022). {Plan de gestión AMP
Namuncurá Banco Burdwood}. {Dirección Nacional de Áreas Marinas
Protegidas (DNAMP), Argentina}.

\bibitem[\citeproctext]{ref-Albert2002}
Albert, R., \& Barabási, A.-L. (2002). Statistical mechanics of complex
networks. \emph{Reviews of Modern Physics}, \emph{74}(1), 47--97.
doi:\href{https://doi.org/10.1103/RevModPhys.74.47}{10.1103/RevModPhys.74.47}

\bibitem[\citeproctext]{ref-Allega2019}
Allega, Lucrecia, Braverman, M. S., Cabreira, A. G., Campodónico, S.,
Colonello, J. H., Derisio, C. M., \ldots{} Verón, E. M. (2019).
\emph{{Estado del conocimiento biológico pesquero de los principales
recursos vivos y su ambiente, con relación a la exploración
hidrocarburífera en la Zona Económica Exclusiva Argentina y
adyacencias}}. {INIDEP}.

\bibitem[\citeproctext]{ref-Allega2020}
Allega, L., Braverman, M., Campodónico, S., Carozza, C. R., Cepeda, G.
D., Colonello, J. H., \ldots{} Verón, E. (2020). \emph{{Estado del
conocimiento biológico pesquero de los principales recursos vivos y su
ambiente, con relación a la exploración hidrocarburífera en la Zona
Económica Exclusiva argentina y sus adyacencias}}. {Mar del Plata}:
{Instituto Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.

\bibitem[\citeproctext]{ref-Anton2019}
Anton, A., Geraldi, N. R., Lovelock, C. E., Apostolaki, E. T., Bennett,
S., Cebrian, J., \ldots{} Duarte, C. M. (2019). Global ecological
impacts of marine exotic species. \emph{Nature Ecology \& Evolution},
\emph{3}(5), 787--800.
doi:\href{https://doi.org/10.1038/s41559-019-0851-0}{10.1038/s41559-019-0851-0}

\bibitem[\citeproctext]{ref-Antoni2020}
Antoni, J. S., Almandoz, G. O., Ferrario, M. E., Hernando, M. P.,
Varela, D. E., Rozema, P. D., \ldots{} Schloss, I. R. (2020). Response
of a natural {Antarctic} phytoplankton assemblage to changes in
temperature and salinity. \emph{Journal of Experimental Marine Biology
and Ecology}, \emph{532}, 151444.
doi:\href{https://doi.org/10.1016/j.jembe.2020.151444}{10.1016/j.jembe.2020.151444}

\bibitem[\citeproctext]{ref-Atkinson2019}
Atkinson, A., Hill, S. L., Pakhomov, E. A., Siegel, V., Reiss, C. S.,
Loeb, V. J., \ldots{} Sailley, S. F. (2019). Krill ({Euphausia} superba)
distribution contracts southward during rapid regional warming.
\emph{Nature Climate Change}, \emph{9}(2), 142--147.
doi:\href{https://doi.org/10.1038/s41558-018-0370-z}{10.1038/s41558-018-0370-z}

\bibitem[\citeproctext]{ref-Atkinson2004}
Atkinson, A., Siegel, V., Pakhomov, E., \& Rothery, P. (2004). Long-term
decline in krill stock and increase in salps within the {Southern
Ocean}. \emph{Nature}, \emph{432}(7013), 100--103.
doi:\href{https://doi.org/10.1038/nature02996}{10.1038/nature02996}

\bibitem[\citeproctext]{ref-Balech2008}
Balech, E., \& Ehrlich, M. D. (2008). {Esquema biogeográfico del Mar
Argentino}.

\bibitem[\citeproctext]{ref-Bartley2019}
Bartley, T. J., McCann, K. S., Bieg, C., Cazelles, K., Granados, M.,
Guzzo, M. M., \ldots{} McMeans, B. C. (2019). Food web rewiring in a
changing world. \emph{Nature Ecology \& Evolution}, \emph{3}(3),
345--354.
doi:\href{https://doi.org/10.1038/s41559-018-0772-3}{10.1038/s41559-018-0772-3}

\bibitem[\citeproctext]{ref-Bauer2022}
Bauer, B., Berti, E., Ryser, R., Gauzens, B., Hirt, M. R., Rosenbaum,
B., \ldots{} Brose, U. (2022). Biotic filtering by species' interactions
constrains food-web variability across spatial and abiotic gradients.
\emph{Ecology Letters}, \emph{25}(5), 1225--1236.
doi:\href{https://doi.org/10.1111/ele.13995}{10.1111/ele.13995}

\bibitem[\citeproctext]{ref-Beauchesne2021}
Beauchesne, D., Cazelles, K., Archambault, P., Dee, L. E., \& Gravel, D.
(2021). On the sensitivity of food webs to multiple stressors.
\emph{Ecology Letters}, \emph{24}(10), 2219--2237.
doi:\href{https://doi.org/10.1111/ele.13841}{10.1111/ele.13841}

\bibitem[\citeproctext]{ref-Belgrano2005}
Belgrano, A., Scharler, S. E. R. C. U. M., Scharler, U. M., Dunne, J.,
\& Ulanowicz, R. E. (2005). \emph{Aquatic {Food Webs}: {An Ecosystem
Approach}}. {OUP Oxford}.

\bibitem[\citeproctext]{ref-Belleggia2017}
Belleggia, M., Giberto, D., \& Bremec, C. (2017). Adaptation of diet in
a changed environment: {Increased} consumption of lobster krill {Munida}
gregaria ({Fabricius}, 1793) by {Argentine} hake. \emph{Marine Ecology},
\emph{38}(4), e12445.
doi:\href{https://doi.org/10.1111/maec.12445}{10.1111/maec.12445}

\bibitem[\citeproctext]{ref-Bovcon2013}
Bovcon, N. D., Góngora, M. E., Marinao, C., \& González-Zevallos, D.
(2013). Composición de las capturas y descartes generados en la pesca de
merluza común {Merluccius} hubbsi y langostino patagónico {Pleoticus}
muelleri: Un caso de estudio en la flota fresquera de altura del {Golfo
San Jorge}, {Chubut}, {Argentina}. \emph{Revista de Biología Marina y
Oceanografía}, \emph{48}(2), 303--319.
doi:\href{https://doi.org/10.4067/S0718-19572013000200010}{10.4067/S0718-19572013000200010}

\bibitem[\citeproctext]{ref-Boyd2015}
Boyd, P. W., Lennartz, S. T., Glover, D. M., \& Doney, S. C. (2015).
Biological ramifications of climate-change-mediated oceanic
multi-stressors. \emph{Nature Climate Change}, \emph{5}(1), 71--79.
doi:\href{https://doi.org/10.1038/nclimate2441}{10.1038/nclimate2441}

\bibitem[\citeproctext]{ref-Braeckman2021}
Braeckman, U., Pasotti, F., Hoffmann, R., Vázquez, S., Wulff, A.,
Schloss, I. R., \ldots{} Vanreusel, A. (2021). Glacial melt disturbance
shifts community metabolism of an {Antarctic} seafloor ecosystem from
net autotrophy to heterotrophy. \emph{Communications Biology},
\emph{4}(1), 148.
doi:\href{https://doi.org/10.1038/s42003-021-01673-6}{10.1038/s42003-021-01673-6}

\bibitem[\citeproctext]{ref-Braithwaite2015}
Braithwaite, J. E., Meeuwig, J. J., Letessier, T. B., Jenner, K. C. S.,
\& Brierley, A. S. (2015). From sea ice to blubber: Linking whale
condition to krill abundance using historical whaling records.
\emph{Polar Biology}, \emph{38}(8), 1195--1202.
doi:\href{https://doi.org/10.1007/s00300-015-1685-0}{10.1007/s00300-015-1685-0}

\bibitem[\citeproctext]{ref-Brown2004}
Brown, J. H., Gillooly, J. F., Allen, A. P., Savage, V. M., \& West, G.
B. (2004). Toward a {Metabolic Theory} of {Ecology}. \emph{Ecology},
\emph{85}(7), 1771--1789.
doi:\href{https://doi.org/10.1890/03-9000}{10.1890/03-9000}

\bibitem[\citeproctext]{ref-Bruder2019}
Bruder, A., Frainer, A., Rota, T., \& Primicerio, R. (2019). The
{Importance} of {Ecological Networks} in {Multiple-Stressor Research}
and {Management}. \emph{Frontiers in Environmental Science}, \emph{7}.

\bibitem[\citeproctext]{ref-Bruno2023}
Bruno, D. O., Riccialdelli, L., Acha, E. M., \& Fernández, D. A. (2023).
Seasonal variation of autochthonous and allochthonous carbon sources for
the first levels of the {Beagle Channel} food web. \emph{Journal of
Marine Systems}, \emph{239}, 103859.
doi:\href{https://doi.org/10.1016/j.jmarsys.2023.103859}{10.1016/j.jmarsys.2023.103859}

\bibitem[\citeproctext]{ref-Chown2022}
Chown, S. L., Leihy, R. I., Naish, T. R., Brooks, C. M., Convey, P.,
Henley, B. J., \ldots{} Grant, S. M. (2022). Antarctic climate change
and the environment: A decadal synopsis and recommendations for action.

\bibitem[\citeproctext]{ref-Ciancio2008}
Ciancio, J. E., Pascual, M. A., Botto, F., Frere, E., \& Iribarne, O.
(2008). Trophic relationships of exotic anadromous salmonids in the
southern {Patagonian Shelf} as inferred from stable isotopes.
\emph{Limnology and Oceanography}, \emph{53}(2), 788--798.
doi:\href{https://doi.org/10.4319/lo.2008.53.2.0788}{10.4319/lo.2008.53.2.0788}

\bibitem[\citeproctext]{ref-Cirtwill2015}
Cirtwill, A. R., Stouffer, D. B., \& Romanuk, T. N. (2015). Latitudinal
gradients in biotic niche breadth vary across ecosystem types.
\emph{Proceedings of the Royal Society B: Biological Sciences},
\emph{282}(1819), 20151589.
doi:\href{https://doi.org/10.1098/rspb.2015.1589}{10.1098/rspb.2015.1589}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[vmargin=1in,hmargin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{pdflscape,booktabs}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage[running]{lineno}
\linenumbers
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\hypertarget{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}{%
\section{The response of trophic interaction networks to multiple
stressors in a marine latitudinal gradient of the Southern
Hemisphere}\label{the-response-of-trophic-interaction-networks-to-multiple-stressors-in-a-marine-latitudinal-gradient-of-the-southern-hemisphere}}

\hypertarget{running-title-marine-stressors-in-the-southern-hemisphere}{%
\subsection{Running Title: Marine stressors in the Southern
Hemisphere}\label{running-title-marine-stressors-in-the-southern-hemisphere}}

@@

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

@@

\hypertarget{introduction}{%
\subsection{1. Introduction}\label{introduction}}

@@

\hypertarget{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}{%
\subsection{2. The structure of marine food webs in the Southwest
Atlantic - Antarctic
region}\label{the-structure-of-marine-food-webs-in-the-southwest-atlantic---antarctic-region}}

@@

\hypertarget{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}{%
\subsection{3. Environmental and anthropogenic stressors in the
Southwest Atlantic - Antarctic
region}\label{environmental-and-anthropogenic-stressors-in-the-southwest-atlantic---antarctic-region}}

@@

\hypertarget{san-jorge-gulf}{%
\subsubsection{3.1 San Jorge Gulf}\label{san-jorge-gulf}}

@@

\hypertarget{beagle-channel}{%
\subsubsection{3.2 Beagle Channel}\label{beagle-channel}}

@@

\hypertarget{burdwood-bank}{%
\subsubsection{3.3 Burdwood Bank}\label{burdwood-bank}}

@@

\hypertarget{scotia-sea}{%
\subsubsection{3.4 Scotia Sea}\label{scotia-sea}}

@@

\hypertarget{potter-cove-antarctica}{%
\subsubsection{3.5 Potter Cove
(Antarctica)}\label{potter-cove-antarctica}}

@@

\hypertarget{weddell-sea-antarctica}{%
\subsubsection{3.6 Weddell Sea
(Antarctica)}\label{weddell-sea-antarctica}}

@@

\hypertarget{from-species-stressors-to-food-web-effects}{%
\subsection{4. From species' stressors to food web
effects}\label{from-species-stressors-to-food-web-effects}}

@@

\hypertarget{main-stressor-effects-in-food-webs-in-a-southwest-atlantic---antarctic-gradient}{%
\subsubsection{4.1 Main stressor effects in food webs in a southwest
Atlantic - Antarctic
gradient}\label{main-stressor-effects-in-food-webs-in-a-southwest-atlantic---antarctic-gradient}}

@@

\hypertarget{gaps-and-future-perspectives}{%
\subsection{5. Gaps and future
perspectives}\label{gaps-and-future-perspectives}}

@@

\hypertarget{conclusions}{%
\subsection{Conclusions}\label{conclusions}}

@@

\hypertarget{acknowledgements}{%
\subsection{Acknowledgements}\label{acknowledgements}}

@@

\hypertarget{references}{%
\subsection*{References}\label{references}}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Acha2004}{}}%
Acha, E. M., Mianzan, H. W., Guerrero, R. A., Favero, M., \& Bava, J.
(2004). Marine fronts at the continental shelves of austral {South
America}: {Physical} and ecological processes. \emph{Journal of Marine
Systems}, \emph{44}(1), 83--105.
doi:\href{https://doi.org/10.1016/j.jmarsys.2003.09.005}{10.1016/j.jmarsys.2003.09.005}

\leavevmode\vadjust pre{\hypertarget{ref-APN2022}{}}%
Administración de Parques Nacionales. (2022). {Plan de gestión AMP
Namuncurá Banco Burdwood}. {Dirección Nacional de Áreas Marinas
Protegidas (DNAMP), Argentina}.

\leavevmode\vadjust pre{\hypertarget{ref-Albert2002}{}}%
Albert, R., \& Barabási, A.-L. (2002). Statistical mechanics of complex
networks. \emph{Reviews of Modern Physics}, \emph{74}(1), 47--97.
doi:\href{https://doi.org/10.1103/RevModPhys.74.47}{10.1103/RevModPhys.74.47}

\leavevmode\vadjust pre{\hypertarget{ref-Allega2019}{}}%
Allega, Lucrecia, Braverman, M. S., Cabreira, A. G., Campodónico, S.,
Colonello, J. H., Derisio, C. M., \ldots{} Verón, E. M. (2019).
\emph{{Estado del conocimiento biológico pesquero de los principales
recursos vivos y su ambiente, con relación a la exploración
hidrocarburífera en la Zona Económica Exclusiva Argentina y
adyacencias}}. {INIDEP}.

\leavevmode\vadjust pre{\hypertarget{ref-Allega2020}{}}%
Allega, L., Braverman, M., Campodónico, S., Carozza, C. R., Cepeda, G.
D., Colonello, J. H., \ldots{} Verón, E. (2020). \emph{{Estado del
conocimiento biológico pesquero de los principales recursos vivos y su
ambiente, con relación a la exploración hidrocarburífera en la Zona
Económica Exclusiva argentina y sus adyacencias}}. {Mar del Plata}:
{Instituto Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.

\leavevmode\vadjust pre{\hypertarget{ref-Anton2019}{}}%
Anton, A., Geraldi, N. R., Lovelock, C. E., Apostolaki, E. T., Bennett,
S., Cebrian, J., \ldots{} Duarte, C. M. (2019). Global ecological
impacts of marine exotic species. \emph{Nature Ecology \& Evolution},
\emph{3}(5), 787--800.
doi:\href{https://doi.org/10.1038/s41559-019-0851-0}{10.1038/s41559-019-0851-0}

\leavevmode\vadjust pre{\hypertarget{ref-Antoni2020}{}}%
Antoni, J. S., Almandoz, G. O., Ferrario, M. E., Hernando, M. P.,
Varela, D. E., Rozema, P. D., \ldots{} Schloss, I. R. (2020). Response
of a natural {Antarctic} phytoplankton assemblage to changes in
temperature and salinity. \emph{Journal of Experimental Marine Biology
and Ecology}, \emph{532}, 151444.
doi:\href{https://doi.org/10.1016/j.jembe.2020.151444}{10.1016/j.jembe.2020.151444}

\leavevmode\vadjust pre{\hypertarget{ref-Atkinson2019}{}}%
Atkinson, A., Hill, S. L., Pakhomov, E. A., Siegel, V., Reiss, C. S.,
Loeb, V. J., \ldots{} Sailley, S. F. (2019). Krill ({Euphausia} superba)
distribution contracts southward during rapid regional warming.
\emph{Nature Climate Change}, \emph{9}(2), 142--147.
doi:\href{https://doi.org/10.1038/s41558-018-0370-z}{10.1038/s41558-018-0370-z}

\leavevmode\vadjust pre{\hypertarget{ref-Atkinson2004}{}}%
Atkinson, A., Siegel, V., Pakhomov, E., \& Rothery, P. (2004). Long-term
decline in krill stock and increase in salps within the {Southern
Ocean}. \emph{Nature}, \emph{432}(7013), 100--103.
doi:\href{https://doi.org/10.1038/nature02996}{10.1038/nature02996}

\leavevmode\vadjust pre{\hypertarget{ref-Balech2008}{}}%
Balech, E., \& Ehrlich, M. D. (2008). {Esquema biogeográfico del Mar
Argentino}.

\leavevmode\vadjust pre{\hypertarget{ref-Bartley2019}{}}%
Bartley, T. J., McCann, K. S., Bieg, C., Cazelles, K., Granados, M.,
Guzzo, M. M., \ldots{} McMeans, B. C. (2019). Food web rewiring in a
changing world. \emph{Nature Ecology \& Evolution}, \emph{3}(3),
345--354.
doi:\href{https://doi.org/10.1038/s41559-018-0772-3}{10.1038/s41559-018-0772-3}

\leavevmode\vadjust pre{\hypertarget{ref-Bauer2022}{}}%
Bauer, B., Berti, E., Ryser, R., Gauzens, B., Hirt, M. R., Rosenbaum,
B., \ldots{} Brose, U. (2022). Biotic filtering by species' interactions
constrains food-web variability across spatial and abiotic gradients.
\emph{Ecology Letters}, \emph{25}(5), 1225--1236.
doi:\href{https://doi.org/10.1111/ele.13995}{10.1111/ele.13995}

\leavevmode\vadjust pre{\hypertarget{ref-Beauchesne2021}{}}%
Beauchesne, D., Cazelles, K., Archambault, P., Dee, L. E., \& Gravel, D.
(2021). On the sensitivity of food webs to multiple stressors.
\emph{Ecology Letters}, \emph{24}(10), 2219--2237.
doi:\href{https://doi.org/10.1111/ele.13841}{10.1111/ele.13841}

\leavevmode\vadjust pre{\hypertarget{ref-Belgrano2005}{}}%
Belgrano, A., Scharler, S. E. R. C. U. M., Scharler, U. M., Dunne, J.,
\& Ulanowicz, R. E. (2005). \emph{Aquatic {Food Webs}: {An Ecosystem
Approach}}. {OUP Oxford}.

\leavevmode\vadjust pre{\hypertarget{ref-Belleggia2017}{}}%
Belleggia, M., Giberto, D., \& Bremec, C. (2017). Adaptation of diet in
a changed environment: {Increased} consumption of lobster krill {Munida}
gregaria ({Fabricius}, 1793) by {Argentine} hake. \emph{Marine Ecology},
\emph{38}(4), e12445.
doi:\href{https://doi.org/10.1111/maec.12445}{10.1111/maec.12445}

\leavevmode\vadjust pre{\hypertarget{ref-Bovcon2013}{}}%
Bovcon, N. D., Góngora, M. E., Marinao, C., \& González-Zevallos, D.
(2013). Composición de las capturas y descartes generados en la pesca de
merluza común {Merluccius} hubbsi y langostino patagónico {Pleoticus}
muelleri: Un caso de estudio en la flota fresquera de altura del {Golfo
San Jorge}, {Chubut}, {Argentina}. \emph{Revista de Biología Marina y
Oceanografía}, \emph{48}(2), 303--319.
doi:\href{https://doi.org/10.4067/S0718-19572013000200010}{10.4067/S0718-19572013000200010}

\leavevmode\vadjust pre{\hypertarget{ref-Boyd2015}{}}%
Boyd, P. W., Lennartz, S. T., Glover, D. M., \& Doney, S. C. (2015).
Biological ramifications of climate-change-mediated oceanic
multi-stressors. \emph{Nature Climate Change}, \emph{5}(1), 71--79.
doi:\href{https://doi.org/10.1038/nclimate2441}{10.1038/nclimate2441}

\leavevmode\vadjust pre{\hypertarget{ref-Braeckman2021}{}}%
Braeckman, U., Pasotti, F., Hoffmann, R., Vázquez, S., Wulff, A.,
Schloss, I. R., \ldots{} Vanreusel, A. (2021). Glacial melt disturbance
shifts community metabolism of an {Antarctic} seafloor ecosystem from
net autotrophy to heterotrophy. \emph{Communications Biology},
\emph{4}(1), 148.
doi:\href{https://doi.org/10.1038/s42003-021-01673-6}{10.1038/s42003-021-01673-6}

\leavevmode\vadjust pre{\hypertarget{ref-Braithwaite2015}{}}%
Braithwaite, J. E., Meeuwig, J. J., Letessier, T. B., Jenner, K. C. S.,
\& Brierley, A. S. (2015). From sea ice to blubber: Linking whale
condition to krill abundance using historical whaling records.
\emph{Polar Biology}, \emph{38}(8), 1195--1202.
doi:\href{https://doi.org/10.1007/s00300-015-1685-0}{10.1007/s00300-015-1685-0}

\leavevmode\vadjust pre{\hypertarget{ref-Brown2004}{}}%
Brown, J. H., Gillooly, J. F., Allen, A. P., Savage, V. M., \& West, G.
B. (2004). Toward a {Metabolic Theory} of {Ecology}. \emph{Ecology},
\emph{85}(7), 1771--1789.
doi:\href{https://doi.org/10.1890/03-9000}{10.1890/03-9000}

\leavevmode\vadjust pre{\hypertarget{ref-Bruder2019}{}}%
Bruder, A., Frainer, A., Rota, T., \& Primicerio, R. (2019). The
{Importance} of {Ecological Networks} in {Multiple-Stressor Research}
and {Management}. \emph{Frontiers in Environmental Science}, \emph{7}.

\leavevmode\vadjust pre{\hypertarget{ref-Bruno2023}{}}%
Bruno, D. O., Riccialdelli, L., Acha, E. M., \& Fernández, D. A. (2023).
Seasonal variation of autochthonous and allochthonous carbon sources for
the first levels of the {Beagle Channel} food web. \emph{Journal of
Marine Systems}, \emph{239}, 103859.
doi:\href{https://doi.org/10.1016/j.jmarsys.2023.103859}{10.1016/j.jmarsys.2023.103859}

\leavevmode\vadjust pre{\hypertarget{ref-Chown2022}{}}%
Chown, S. L., Leihy, R. I., Naish, T. R., Brooks, C. M., Convey, P.,
Henley, B. J., \ldots{} Grant, S. M. (2022). Antarctic climate change
and the environment: A decadal synopsis and recommendations for action.
